Data Management Plan

### 2021-11-29 application/dataManagementPlan_long.tex
Added reference to BonZeb and header of instructions

@@

The proposed enhancements to the Bonsai ecosystem will impact a wide range of
existing and to-be-created datasets collected by open-source initiatives
already integrated into the Bonsai ecosystem. For example, datasets of feeding
behaviour in flies (collected with FlyPAD
sensors\footnote{\url{https://flypad.rocks/}}), electrophysiology datasets
(collected with products supported by
OpenEphys\footnote{\url{https://open-ephys.org/}}), datasets of vivo imaging of
brain activity (collected with the UCLA
Miniscope\footnote{\url{http://miniscope.org/}} or with NeuroPhotometrics
products\footnote{\url{https://neurophotometrics.com/}}), datasets using rich
2D or 3D visual environments (created with
BonVision\footnote{\url{https://bonvision.github.io/}}), high-density
electrophysiology datasets (recorded with NeuroPixels
probes\footnote{\url{https://www.neuropixels.org/}}), and animal behavioral
datasets (with body parts tracked with
DeepLabCut\footnote{\url{http://www.mackenziemathislab.org/deeplabcut}}).

>>>>

\textcolor{orange}{\textit{The following template is provided to applicants to assist in the development of a Data Management Plan (DMP) to accompany a research proposal. The notes (in italics) provide further context and guidance for its completion and should be deleted prior to submission. Applicants should consider submission of a DMP which is proportional to the quantity and nature of the data. Where substantial data is generated from the research, it is expected that the DMP will be longer and more detailed than studies generating small amounts of data, where DMPs may be significantly shorter. In either case, the DMP should be a maximum of 3 pages in length.}}

@@

The proposed enhancements to the Bonsai ecosystem will impact a wide range of
existing and to-be-created datasets collected by open-source initiatives
already integrated into the Bonsai ecosystem. For example, datasets of feeding
behaviour in flies (collected with FlyPAD
sensors\footnote{\url{https://flypad.rocks/}}), high-resolution zebrafish
tracking datasets (collected with
BonZeb\footnote{\url{https://github.com/ncguilbeault/BonZeb/}}),
electrophysiology datasets (collected with products supported by
OpenEphys\footnote{\url{https://open-ephys.org/}} or with NeuroPixels
probes\footnote{\url{https://www.neuropixels.org/}})), datasets of in-vivo
imaging of brain activity (collected with the UCLA
Miniscope\footnote{\url{http://miniscope.org/}} or with NeuroPhotometrics
products\footnote{\url{https://neurophotometrics.com/}}), datasets using rich
2D or 3D visual environments (created with
BonVision\footnote{\url{https://bonvision.github.io/}}), and animal behavioral
datasets (with body parts tracked with
DeepLabCut\footnote{\url{http://www.mackenziemathislab.org/deeplabcut}}).

### 2021-11-29 application/dataManagementPlan_short.tex
Added reference to BonZeb and header of instructions

% \usepackage[colorlinks=true]{hyperref}
\usepackage[colorlinks = true,
            linkcolor = blue!50!black!50,
            urlcolor  = blue!50!black!50,
            citecolor = blue!50!black!50,
            anchorcolor = blue!50!black!50]{hyperref}
\usepackage[super]{natbib}
\renewcommand{\citet}[1]{[\citenum{#1}]}
% \usepackage{apalike}
\usepackage{graphicx}
\usepackage{verbatim}

@@

The proposed enhancements to the Bonsai ecosystem will impact a wide range of
existing and to-be-created datasets collected by open-source initiatives
already integrated into the Bonsai ecosystem. For example, datasets of feeding
behaviour in flies (collected with FlyPAD
sensors\footnote{\url{https://flypad.rocks/}}), electrophysiology datasets
(collected with products supported by
OpenEphys\footnote{\url{https://open-ephys.org/}} or with NeuroPixels
probes\footnote{\url{https://www.neuropixels.org/}})), datasets of in-vivo
imaging of brain activity (collected with the UCLA
Miniscope\footnote{\url{http://miniscope.org/}} or with NeuroPhotometrics
products\footnote{\url{https://neurophotometrics.com/}}), datasets using rich
2D or 3D visual environments (created with
BonVision\footnote{\url{https://bonvision.github.io/}}), and animal behavioral
datasets (with body parts tracked with
DeepLabCut\footnote{\url{http://www.mackenziemathislab.org/deeplabcut}}).

@@

>>>>

% \usepackage[colorlinks=true]{hyperref}
\usepackage[colorlinks = true,
            linkcolor = blue!50!black!50,
            urlcolor  = blue!50!black!50,
            citecolor = blue!50!black!50,
            anchorcolor = blue!50!black!50]{hyperref}
% \usepackage[super]{natbib}
% \renewcommand{\citet}[1]{[\citenum{#1}]}
\usepackage{natbib}
\usepackage{apalike}
\usepackage{graphicx}
\usepackage{verbatim}

@@

The proposed enhancements to the Bonsai ecosystem will impact a wide range of
existing and to-be-created datasets collected by open-source initiatives
already integrated into the Bonsai ecosystem. For example, datasets of feeding
behaviour in flies (collected with FlyPAD
sensors\footnote{\url{https://flypad.rocks/}}), high-resolution zebrafish
tracking datasets (collected with
BonZeb\footnote{\url{https://github.com/ncguilbeault/BonZeb/}}),
electrophysiology datasets (collected with products supported by
OpenEphys\footnote{\url{https://open-ephys.org/}} or with NeuroPixels
probes\footnote{\url{https://www.neuropixels.org/}})), datasets of in-vivo
imaging of brain activity (collected with the UCLA
Miniscope\footnote{\url{http://miniscope.org/}} or with NeuroPhotometrics
products\footnote{\url{https://neurophotometrics.com/}}), datasets using rich
2D or 3D visual environments (created with
BonVision\footnote{\url{https://bonvision.github.io/}}), and animal behavioral
datasets (with body parts tracked with
DeepLabCut\footnote{\url{http://www.mackenziemathislab.org/deeplabcut}}).

@@

% \bibliographystyle{unsrtveryabbrv}
\bibliographystyle{apalike}
\bibliography{bonsai}
